Why Donors Donate: Disentangling Organizational and Structural Heuristics for International Philanthropy

### 2023-11-20 manuscript/manuscript.qmd
Final Suparna edits

Over the last two decades, governments globally have increasingly cracked down on NGOs [@ChristensenWeinstein:2013; @DupuyRonPrakash:2016; @Heiss:2017; @GlasiusSchalkDeLange:2020; @BakkeMitchellSmidt:2020; @Chaudhry:2022]. Repressive governments have cracked down on these organizations using both violence, as well as administrative crackdown, which create barriers to funding and advocacy for a variety of NGOs [@DupuyRonPrakash:2016; @Chaudhry:2022]. Policymakers have referred to this phenomenon as the "closing of civic space" or "shrinking civic space" [@CarothersBrechenmacher:2014; @Rutzen:2015] and data from the CIVICUS Civil Society Monitor shows that civil society groups face serious restrictions in more than 60% of countries---117 in total [@CIVICUSMonitor]. These attacks---most of which have been implemented through anti-NGO laws---have adversely affected the ability of both domestic and international NGOs to operate and raise funds. Official aid funds have decreased substantially in countries that have imposed restrictive anti-NGO legislation [@ChaudhryHeiss:2018; @DupuyPrakash:2018] and official aid donors channel fewer funds to contentious issues and instead choose to fund "tame" causes [@ChaudhryHeiss:2018; @Bush:2015; @Herrold:2020; @RightSpringmanWibbels:2022]. In response to this dramatic shift in the NGO funding landscape, international NGOs (INGOs) have increasingly turned to foreign individual donors to offset the loss of funding from government and foundation sources [@BanksHulmeEdwards:2015].

The amount of private foreign aid is not insignificant---from 2000--2010, private giving by U.S. entities towards international causes doubled in real terms [@DesaiKharas:2018, 505]. In 2016, U.S. private philanthropy towards international NGOs amounted to \$22.06 billion [@GivingUSA:2017]. Most notably, a large portion of this growth was driven by individuals making small-scale donations. In 2017, individuals gave \$286.7 billion or approximately 70% of total giving to international affairs. This further increased to \$427.71 billion in 2018, 85.7% of which was through individuals [@GivingUSA:2019]. This turn to private donors opens INGOs up to new dynamics in seeking out funds. Many organizations that had previously relied on governments and foundations had optimized their fundraising strategies for those donors, but now need to tailor their fundraising strategies to private individuals, who behave differently from governments and foundations.

Individual donors have different preferences and rely on signals of effectiveness that differ from the benchmarks that large donor agencies rely on. While INGOs have control over these organizational-level factors such as financial transparency and accountability that motivate donations, the political environment in the host countries INGOs work in---including the global crackdown on civil society that is causing many organizations to seek out private funding in the first place---is a structural factor that INGOs can rarely influence on their own. How do organizational elements of private donor decision-making interact with broader structural limits on INGO fundraising? How do individual donors in the U.S. feel about donating to legally besieged NGOs abroad? How do organizational-level factors such as financial transparency and accountability compare with more structural-level factors such as host country civic environments when deciding to donate?

Existing research shows that organizational accountability and financial transparency play an important role in motivating individual donors to donate to NGOs [@HarrisNeely:2021; @SaxtonKuoHo:2012; @Vaccaro:2006; @VaccaroMadsen:2006; @Tremblay-BoirePrakash:2017; @Becker:2018]. We extend this literature by evaluating how these organization-level characteristics influence private donor behavior in an era of shrinking civic space. In considering this question, we engage with a growing body of research on the consequences of closing civic space on NGOs and donors [@DupuyPrakash:2018; @RightSpringmanWibbels:2022; @FransenDupuyHinfelaar:2021; @SundstromHenrySperling:2022; @Herrold:2020; @ChaudhryHeiss:2021]. We argue that NGO-level organizational factors and domestic political environments of NGO host countries serve as heuristics and can influence foreign private donors' preferences. We fielded a conjoint experiment to a nationally representative sample of 1,016 adults in the US, which allows us to directly compare the relative impact of host government repression of NGOs and organizational financial transparency and accountability on individual donor preferences. The result of this experiment shows that both financial transparency and accountability increase individuals' willingness to donate to NGOs. Conversely, learning about host government criticism and crackdown against NGOs decreases the likelihood of donation by itself; however, organizational features such as financial transparency and accountability can protect against this dampening effect. These effect sizes are substantial: our key treatment effects have a magnitude of around ten percentage points in the predicted probability of choosing to donate to an NGO.

@@

The third wave of democratization, the collapse of the Soviet Union, and the spread of a "pro-NGO norm" led to an increased role and visibility for NGOs. Globally, a large amount of official aid resources were channeled to NGOs focusing on service provision and development. Public and private donors perceived these organizations as more efficient than states with weak institutions and poor governance; there was a high risk that such states would use aid transfers inefficiently [@Dietrich:2013]. Less bureaucratic and more nimble than state institutions, NGOs were seen as key agents of development and democratization [@Herrold:2020, 142--43].

@@

In theory, donors should scrutinize each aspect of an NGO's organizational structure and programmatic performance prior to donation, but this rarely happens in practice [@Tremblay-BoirePrakash:2017]. Instead, individuals rely on heuristics to simplify their decision-making. One heuristic for potential donors is organizational efficacy or the belief that an individual's donation will make a real difference [@ChaudhryHeiss:2021]. This can manifest itself through multiple mechanisms such as the amount an organization spends on overhead costs, whether an organization makes its finances public, or whether an organization participates in voluntary accountability practices, such as listing organizational details on websites like GuideStar and Charity Navigator.

@@

Previous research has found that media exposés about charity mismanagement can generate negative reputational spillovers for the charitable sector [@GibelmanGelman:2004]. Diversions, or the unauthorized use of an organization's assets, including embezzlement and theft can result in a decrease in donations. This effect becomes even stronger with media coverage of diversion [@HarrisPetrovitsYetman:2023]. Organizational financial transparency can reduce actual or perceived information asymmetries between donors and charities, thus potentially increasing donor likelihood of donating to an INGO.

@@

Explaining actions to stakeholders can be important because many NGOs, even when well-intentioned ones, can devote excessive resources towards marketing and overheads [@Bowman:2006]. Private donors, subsequently, may be more likely to dislike NGOs that spend a large share of their revenues for unproductive purposes [@Rose-Ackerman:1982], or rather, a large share of resources on administration, management and fundraising. Lack of accountability is associated with lesser public trust, reputation, perceived quality and donation behavior [@Becker:2018]. As @Tremblay-BoirePrakash:2017 point out, while individuals would like to have some assurance that their resources will be used appropriately and organizations are not spending too much on overhead, donors do not necessarily have the time to research charities thoroughly.

@@

The changes in civic environments impacting NGO activity have also influenced official donor responses. Scholars have found that while multilateral donors do not reduce aid following the passage of anti-NGO laws, they are associated with a 32% decline in bilateral aid inflows [@DupuyPrakash:2018]. Further, advocacy-oriented donors---i.e., those that fund democracy and civil society promotion activities---reduced their spending by 74%, but did not cut their spending on development projects such as education, health, water, and sanitation [@RightSpringmanWibbels:2022]. However, previous literature has established that individual private donors may not necessarily use the same metrics as official donors when deciding to donate [@DesaiKharas:2018; @ChaudhryHeiss:2021]. Private foreign aid does not have to deal with the same strategic and political considerations as official aid and therefore, may be in a better position to respond to recipients' needs on the grounds [@EasterlyWilliamson:2011]. These anti-NGO laws may signal to private donors that NGOs undertake crucial work abroad, which is why governments perceive them as threatening and crack down on them. Therefore, we expect that government restrictions abroad will increase respondents' likelihood of donating to the organization.

@@

Finally, organization funding source also serves as a reliable donor heuristic. Organizations that are funded by many small donors are substantially more popular than those funded by government grants or a small group of wealthy donors---when compared to many small donors, both government and wealthy individual funding cause `r amce$funded_primarily_by_government_grants$pp_abs` and `r amce$funded_primarily_by_a_handful_of_wealthy_private_donors$pp_abs` percentage point decreases in the probability of selection (`r amce$funded_primarily_by_government_grants$nice_ci_pd` and `r amce$funded_primarily_by_a_handful_of_wealthy_private_donors$nice_ci_pd`). These effects follow existing research on donor efficacy [@ChaudhryHeiss:2021]---when donors know that an organization is funded by others like themselves and that the marginal benefit of their individual donation is important, they are more likely to donate. In contrast, when donors know that an organization's funding does not come from the public and instead comes from a few wealthy donors or large government grants, the marginal benefit they receive from donating decreases and they are less likely to donate. Donors therefore appear to be motivated by some degree of personal efficacy.

@@

Having explored the effects of general organizational characteristics on the propensity to donate, we can test our first hypotheses and examine the effects of our treatments of interest. As seen in the marginal means in @fig-all-results, both transparency and accountability are surprisingly strong signals of organizational deservingness. Respondents strongly prefer organizations that engage in either transparency or accountability---both treatments have a posterior marginal mean of roughly 30% compared to a baseline equally-at-random probability of 25% (transparency: `r mms$transparency_yes$nice_simple`; accountability: `r mms$accountability_yes$nice_simple`). The AMCEs for each treatment show a roughly 10 percentage point increase in the probability of selection compared to organizations that do not engage in transparency or accountability (transparency: `r amce$transparency_yes$nice_full`; accountability: `r amce$accountability_yes$nice_full`). This effect is nearly the same order of magnitude as the Red Cross effect---an NGO that chooses to be more transparent or that takes steps to demonstrate greater accountability can expect to see an increase in the probability of selection equivalent to the boost of the brand name effect associated with the Red Cross. As predicted, we thus find strong support for both H~1a~ and H~1b~: if NGOs are financially transparent or engage in accountability practices, then individual private donors are roughly 10 percentage points more likely to donate to them. Donors appear to reward NGOs for their efforts to disclose their funding and be more transparent.

@@

To test our second hypothesis regarding structural heuristics, we explore the effect of an NGO's host country conditions on the propensity to donate. Contrary to our expectations, respondents appear to prefer donating to NGOs that have friendly relationships with their host governments, with a marginal mean of `r mms$friendly_relationship_with_government$pct` (compared to a baseline of 25%; `r mms$friendly_relationship_with_government$nice_ci`). Respondents are less likely to donate when an organization is criticized by its host government, and far less likely when an organization faces crackdown. Compared to other treatments, an organization facing crackdown has roughly the same negative preference as an organization without transparency or accountability measures, while having a friendly relationship is generally equivalent to engaging in transparency or accountability.

@@

Over recent years, governments globally have systematically controlled and repressed NGOs using both violent tactics and legal means---a phenomenon known as "closing" or "shrinking" civic space. This trend of closing civic space has important implications for local and international NGOs as well as donors. Recent research has analyzed the impact of this crackdown on public or official aid donors [@DupuyPrakash:2018; @Herrold:2020; @RightSpringmanWibbels:2022]. However, we know relatively little about how state repression of NGOs affects the preferences of foreign private donors [@ChaudhryHeiss:2021]. Unlike state donors, individual and elite donors may not necessarily withdraw or reduce support for NGOs facing harassment abroad. This is important because private philanthropy towards organizations working in international affairs continues to grow despite inflation---from 2021 to 2022, individual giving to nonprofits in international affairs grew by over 10.9% in the US [@GivingUSA:2023].

Given the increasing hurdles faced by these nonprofits, how do individual donors in the U.S. feel about donating to legally besieged NGOs abroad? How do organizational-level factors such as financial transparency and accountability compare with more structural-level factors such as host country civic environments when deciding to donate? We argue that informational heuristics about NGOs’ legal and political environments and organizational-level attributes can influence donor preferences for international giving. Using a conjoint experiment with a nationally representative sample of the U.S. population, we find that both financial transparency and accountability increases individuals' willingness to donate NGOs. Learning about host government criticism and crackdown against NGOs decreases the likelihood of donation by itself; however, organizational features such as financial transparency and accountability protect against this dampening effect, increasing the probability of philanthropic domations by nine percentage points under the worst conditions of legal crackdown. Our results highlight the importance of organizational characteristics like transparency and accountability even in an era of closing civic space.

These results have important implications for NGO operations, fundraising, and survivability at a time when many INGOs are dealing with hostile host governments. A comparison of the effects of these organizational and structural factors is critical to NGO fundraising---while NGOs have control over transparency and accountability, as well as public perception of these organizational characteristics, they may little to no control over host government crackdowns over their organizations. As a result, they may need to rely entirely on improving individual donor perception of organizational transparency and accountability, its impact on NGO operations and the need for private donor funds at a time of shrinking civic space. This article thus provides insight into the importance of different framing or informational heuristics that can motivate such individual donor giving.

>>>>

Over the last two decades, governments globally have increasingly cracked down on NGOs [@ChristensenWeinstein:2013; @DupuyRonPrakash:2016; @Heiss:2017; @GlasiusSchalkDeLange:2020; @BakkeMitchellSmidt:2020; @Chaudhry:2022]. Repressive governments have cracked down on these organizations using both violence, as well as administrative crackdown, which create barriers to funding and advocacy for a variety of NGOs [@DupuyRonPrakash:2016; @Chaudhry:2022]. Policymakers have referred to this phenomenon as the "closing of civic space" or "shrinking civic space" [@CarothersBrechenmacher:2014; @Rutzen:2015]. Data from the CIVICUS Civil Society Monitor shows that civil society groups face serious restrictions in more than 60% of countries---117 in total [@CIVICUSMonitor]. These attacks---most of which have been implemented through anti-NGO laws---have adversely affected the ability of both domestic and international NGOs to operate and raise funds. Official aid funds have decreased substantially in countries that have imposed restrictive anti-NGO legislation [@ChaudhryHeiss:2018; @DupuyPrakash:2018] and official aid donors channel fewer funds to contentious issues such as human rights, elections, and advocacy, and instead choose to fund "tame" causes bush as health, education, and development, among others [@ChaudhryHeiss:2018; @Bush:2015; @Herrold:2020; @RightSpringmanWibbels:2022]. In response to this dramatic shift in the NGO funding landscape, international NGOs (INGOs) have increasingly turned to individual donors abroad to offset the loss of funding from government and foundation sources [@BanksHulmeEdwards:2015].

The amount of private foreign aid is not insignificant---from 2000--2010, private giving by U.S. entities towards international causes doubled in real terms [@DesaiKharas:2018, 505]. In 2016, U.S. private philanthropy towards international NGOs amounted to \$22.06 billion [@GivingUSA:2017]. Most notably, a large portion of this growth was driven by individuals making small-scale donations. In 2017, individuals gave \$286.7 billion or approximately 70% of total giving to international affairs. This further increased to \$427.71 billion in 2018, 85.7% of which was through individuals [@GivingUSA:2019]. This turn to private donors opens INGOs up to new dynamics in seeking out funds. Many organizations that had previously relied on governments and foundations had optimized their fundraising strategies for those donors. But individual donors may behave differently from governments and foundations, so INGOs need to adapt their fundraising strategies to a different set of potential donors.

Individual donors have different preferences and rely on signals of effectiveness that differ from the benchmarks that large donor agencies rely on. While INGOs have control over organizational-level factors such as financial transparency and accountability that motivate donations, the political environment in the host countries INGOs work in---including the global crackdown on civil society that is causing many organizations to seek out private funding in the first place---is a structural factor that INGOs can rarely influence on their own. How do organizational elements of private donor decision-making interact with broader structural limits on INGO fundraising? How do individual donors in the U.S. feel about donating to legally besieged NGOs abroad? How do organizational-level factors such as financial transparency and accountability compare with more structural-level factors such as host country civic environments when deciding to donate?

Existing research shows that organizational accountability and financial transparency play an important role in motivating individual donors to donate to NGOs [@HarrisNeely:2021; @SaxtonKuoHo:2012; @Vaccaro:2006; @VaccaroMadsen:2006; @Tremblay-BoirePrakash:2017; @Becker:2018]. We extend this literature by evaluating how these organization-level characteristics influence private donor behavior in an era of shrinking civic space. In considering this question, we engage with a growing body of research on the consequences of closing civic space on NGOs and donors [@DupuyPrakash:2018; @RightSpringmanWibbels:2022; @FransenDupuyHinfelaar:2021; @SundstromHenrySperling:2022; @Herrold:2020; @ChaudhryHeiss:2021]. We argue that NGO-level organizational factors and domestic political environments of NGO host countries serve as heuristics and can influence foreign private donors' preferences.

We fielded a conjoint experiment to a nationally representative sample of 1,016 adults in the US, which allows us to directly compare the relative impact of host government repression of NGOs and organizational financial transparency and accountability on individual donor preferences. The result of this experiment shows that both financial transparency and accountability increase individuals' willingness to donate to NGOs. Conversely, learning about host government criticism and crackdown against NGOs decreases the likelihood of donation by itself; however, organizational features such as financial transparency and accountability can protect against this dampening effect. These effect sizes are substantial: our key treatment effects have a magnitude of around ten percentage points in the predicted probability of choosing to donate to an NGO.

@@

The third wave of democratization, the collapse of the Soviet Union, and the spread of a "pro-NGO norm" led to an increased role and visibility for NGOs [@Reimann:2006]. Globally, a large amount of official aid resources were channeled to NGOs focusing on service provision and development. Public and private donors perceived these organizations as more efficient than states with weak institutions and poor governance; there was a high risk that such states would use aid transfers inefficiently [@Dietrich:2013]. Less bureaucratic and more nimble than state institutions, NGOs were seen as key agents of development and democratization [@Herrold:2020, 142--43].

@@

In theory, donors should scrutinize each aspect of an NGO's organizational structure and programmatic performance prior to donation, but this rarely happens in practice [@Tremblay-BoirePrakash:2017]. Instead, individuals rely on heuristics to simplify their decision-making. One heuristic for potential donors is organizational efficacy or the belief that an individual's donation will make a real difference [@ChaudhryHeiss:2021]. This can manifest itself through multiple mechanisms such as the amount an organization spends on overhead costs, whether it makes its finances public, or whether it participates in voluntary accountability practices, such as listing organizational details on websites like GuideStar and Charity Navigator.

@@

Previous research has found that media exposés about charity mismanagement can generate negative reputational spillovers for the charitable sector [@GibelmanGelman:2004]. Diversions, or the unauthorized use of an organization's assets, including embezzlement and theft can result in a decrease in donations. This effect becomes even stronger with media coverage of diversion [@HarrisPetrovitsYetman:2023]. Organizational financial transparency can reduce actual or perceived information asymmetries between donors and charities, thus potentially increasing an individual's likelihood of donating to an INGO.

@@

Explaining actions to stakeholders can be important because many NGOs, even well-intentioned ones, can devote excessive resources towards marketing and overheads [@Bowman:2006]. Private donors, subsequently, may be more likely to dislike NGOs that spend a large share of their revenues for unproductive purposes [@Rose-Ackerman:1982], or rather, a large share of resources on administration, management and fundraising. Lack of accountability is associated with lesser public trust, reputation, perceived quality and donation behavior [@Becker:2018]. As @Tremblay-BoirePrakash:2017 point out, while individuals would like to have some assurance that their resources will be used appropriately and organizations are not spending too much on overhead, donors do not necessarily have the time to research charities thoroughly.

@@

The changes in civic environments impacting NGO activity have also influenced official donor responses. Scholars have found that while multilateral donors do not reduce aid following the passage of anti-NGO laws, these laws are associated with a 32% decline in bilateral aid inflows [@DupuyPrakash:2018]. Further, advocacy-oriented donors---i.e., those that fund democracy and civil society promotion activities---reduced their spending by 74%, but did not cut their spending on development projects such as education, health, water, and sanitation [@RightSpringmanWibbels:2022]. However, previous literature has established that individual private donors may not necessarily use the same metrics as official donors when deciding to donate [@DesaiKharas:2018; @ChaudhryHeiss:2021]. Private foreign aid does not have to deal with the same strategic and political considerations as official aid and therefore, may be in a better position to respond to recipients' needs on the grounds [@EasterlyWilliamson:2011]. These anti-NGO laws may signal to private donors that NGOs undertake crucial work abroad, which is why governments perceive them as threatening and crack down on them. Therefore, we expect that government restrictions abroad will increase respondents' likelihood of donating to the organization.

@@

Finally, an organization's primary funding source also serves as a reliable donor heuristic. Organizations that are funded by many small donors are substantially more popular than those funded by government grants or a small group of wealthy donors---when compared to many small donors, both government and wealthy individual funding cause `r amce$funded_primarily_by_government_grants$pp_abs` and `r amce$funded_primarily_by_a_handful_of_wealthy_private_donors$pp_abs` percentage point decreases in the probability of selection (`r amce$funded_primarily_by_government_grants$nice_ci_pd` and `r amce$funded_primarily_by_a_handful_of_wealthy_private_donors$nice_ci_pd`). These effects follow existing research on donor efficacy [@ChaudhryHeiss:2021]---when donors know that an organization is funded by others like themselves and that the marginal benefit of their individual donation is important, they are more likely to donate. In contrast, when donors know that an organization's funding does not come from the public and instead comes from a few wealthy donors or large government grants, the marginal benefit they receive from donating decreases and they are less likely to donate. Donors therefore appear to be motivated by some degree of personal efficacy.

@@

Having explored the effects of general organizational characteristics on the propensity to donate, we can test our first hypotheses and examine the effects of our treatments of interest. As seen in the marginal means in @fig-all-results, both transparency and accountability are strong signals of organizational deservingness. Respondents strongly prefer organizations that engage in either transparency or accountability---both treatments have a posterior marginal mean of roughly 30% compared to a baseline equally-at-random probability of 25% (transparency: `r mms$transparency_yes$nice_simple`; accountability: `r mms$accountability_yes$nice_simple`). The AMCEs for each treatment show a roughly 10 percentage point increase in the probability of selection compared to organizations that do not engage in transparency or accountability (transparency: `r amce$transparency_yes$nice_full`; accountability: `r amce$accountability_yes$nice_full`). This effect is nearly the same order of magnitude as the Red Cross effect---an NGO that chooses to be more transparent or that takes steps to demonstrate greater accountability can expect to see an increase in the probability of selection equivalent to the boost of the brand name effect associated with the Red Cross. As predicted, we thus find strong support for both H~1a~ and H~1b~: if NGOs are financially transparent or engage in accountability practices, then individual private donors are roughly 10 percentage points more likely to donate to them. Donors appear to reward NGOs for their efforts to disclose their funding and be more transparent.

@@

To test our second hypothesis regarding structural heuristics, we explore the effect of an NGO's host country conditions on the propensity to donate. Contrary to our expectations, respondents appear to prefer donating to NGOs that have friendly relationships with their host governments, with a marginal mean of `r mms$friendly_relationship_with_government$pct` (compared to a baseline of 25%; `r mms$friendly_relationship_with_government$nice_ci`). Respondents are less likely to donate when an organization is criticized by its host government, and far less likely when an organization faces crackdown. Compared to other treatments, an organization facing crackdown elicits a similar negative preference among potential donors as an organization without transparency or accountability measures. However, an organization with a friendly relationship with the host government leads potential donors to perceive it as equivalent to engaging in transparency or accountability.

@@

Over recent years, governments globally have systematically controlled and repressed NGOs using both violent tactics and legal means---a phenomenon known as "closing" or "shrinking" civic space. This trend of closing civic space has important implications for local and international NGOs as well as donors. Recent research has analyzed the impact of this crackdown on public or official aid donors [@DupuyPrakash:2018; @Herrold:2020; @RightSpringmanWibbels:2022]. However, we know relatively little about how state repression of NGOs affects the preferences of foreign private donors [@ChaudhryHeiss:2021]. Unlike state donors, individual donors have different motivations for engaging in philanthropy, and they may not necessarily withdraw or reduce support for NGOs facing harassment abroad. This is important because private philanthropy towards organizations working in international affairs continues to grow despite inflation---from 2021 to 2022, individual giving to nonprofits in international affairs grew by over 10.9% in the US [@GivingUSA:2023].

Given the increasing hurdles faced by these nonprofits, how do individual donors in the U.S. feel about donating to legally besieged NGOs abroad? How do organizational-level factors such as financial transparency and accountability compare with more structural-level factors such as host country civic environments when deciding to donate? We argue that informational heuristics about NGOs’ legal and political environments and organizational-level attributes can influence donor preferences for international giving. Using a conjoint experiment with a nationally representative sample of the U.S. population, we find that both financial transparency and accountability increases individuals' willingness to donate to NGOs. Learning about host government criticism and crackdown against NGOs decreases the likelihood of donation by itself; however, organizational features such as financial transparency and accountability protect against this dampening effect, increasing the probability of philanthropic domations by nine percentage points under the worst conditions of legal crackdown. Our results highlight the importance of organizational characteristics like transparency and accountability even in an era of closing civic space.

These results have important implications for NGO operations, fundraising, and survivability at a time when many INGOs are dealing with hostile host governments. A comparison of the effects of these organizational and structural factors is critical to NGO fundraising---while NGOs have control over transparency and accountability, as well as public perception of these organizational characteristics, they have little to no control over host government crackdowns over their organizations. As a result, they may need to rely entirely on improving individual donor perceptions of organizational transparency and accountability and emphasizing the need for private donor funds at a time of shrinking civic space. This article thus provides insight into the importance of different framing or informational heuristics that can motivate such individual donor giving.
